---
title: "INDIVIDUAL ASSESSMENT"
author: "LOVETH NWAKAMMA"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---
# load Train and Test Data 

```{r}
train <- read.csv("C:/Users/lnwak/OneDrive/Desktop/PGD B.A & BD CLASSES/SEM2/PD&PRC/assessment 2/train.csv")

test <- read.csv("C:/Users/lnwak/OneDrive/Desktop/PGD B.A & BD CLASSES/SEM2/PD&PRC/assessment 2/test.csv")
```

# logistics regression on train data with selected variables
```{r}
logistic_model <- glm(y ~ job + education + age + default + balance + loan + contact + campaign + duration + poutcome, data =train, family = 'binomial')
summary(logistic_model)
```
# Display column names
```{r}
names(train)
```

# summary of no of subscribers and non-subscribers from past campaign in train data
```{r}
table(train$y)
```

# en-coding variables from train Data
```{r}
train$y = as.factor(train$y)
train$marital=as.factor(train$marital)
train$job=as.factor(train$job)
train$education= as.factor(train$education)
train$poutcome =as.factor(train$poutcome)
train$default= as.factor(train$default)
train$loan =as.factor(train$loan)
train$contact = as.factor(train$contact)
train$month =as.factor(train$month)
train$day =as.factor(train$day)
```

# en-coding variables from test Data
```{r}
test$y = as.factor(test$y)
test$marital=as.factor(test$marital)
test$job=as.factor(test$job)
test$education= as.factor(test$education)
test$poutcome =as.factor(test$poutcome)
test$default= as.factor(test$default)
test$loan =as.factor(test$loan)
test$contact = as.factor(test$contact)
test$month =as.factor(test$month)
test$day =as.factor(test$day)
```

loading Caret
```{r}
library(caret)
```


# predicting Logistics regression on Test Data
```{r}
predict_model1 <- predict(logistic_model, test, type = "response")
```

```{r}
predict_model1_class <- ifelse(predict_model1 >0.25, 1, 0)
test$predict_model1_class = predict_model1_class
confusionMatrix(as.factor(test$predict_model1_class), as.factor(test$y))
```


#2. Decision Tree Model

#loading library rpart

```{r}
library(rpart)
```

```{r}
library(rpart.plot)
```

#Decision tree with train data
```{r}
tree <- rpart(formula = y ~ job + education + age + default + balance + housing + loan + contact + campaign + duration + poutcome,data = train, minsplit =5, minbucket = 10, control = list(minbucket =10, maxdepth =4), method = 'class', cp = 0.004) 
rpart.plot(tree)
```

# decision tree for test data  

```{r}
tree2 <- rpart(formula = y ~ job + education + age + default + balance + housing + loan + contact + campaign + duration + poutcome,data = test, minsplit =5, minbucket = 10, control = list(minbucket =10, maxdepth =4), method = 'class', cp = 0.004) 
rpart.plot(tree)
```
#predict with test Data
```{r}
predictCART_test = predict(tree2,data=test, type= "class")
test$predictCART_test = predictCART_test
confusionMatrix(test$predictCART_test,as.factor(test$y))
```
#install and load randomforest package
```{r}
library(randomForest)
```

# run random forest on train data
```{r}
random_forest_class = randomForest(y ~ job + education + age + default + balance + housing + loan + contact + campaign + duration + poutcome, data = train,importance = T)
```

# predict random forest on train data
```{r}
P1 <- predict(random_forest_class, train)
confusionMatrix(P1, train$y)
```

#predict with test data

```{r}
random_forest_class2 = randomForest(y ~ job + education + age + default + balance + housing + loan + contact + campaign + duration + poutcome, data = test,importance = T)

P2 <- predict(random_forest_class2, test)
confusionMatrix(P2, test$y)
```
#plot random forest
```{r}
plot(random_forest_class2)
```
# sort out the most important variables towards predicting the bank data outcome
```{r}
varImpPlot(random_forest_class2)
```
# load pRoc
```{r}
library(pROC)
```

#run Roc on each predicted test data for LR,DT, and RF 
```{r}
roc1 <- roc(as.numeric(test$y),as.numeric(predict_model1_class))
```

```{r}
roc2 <- roc(as.numeric(test$y),as.numeric(predictCART_test))
```

```{r}
roc3 <- roc(as.numeric(test$y),as.numeric(P2))
```

#plot ROC to justify choosen model
```{r}
plot(roc1, col="blue", legacy.axes=TRUE, main="ROC Curve Comparison", xlab="False Positive Rate", ylab="True Positive Rate")
plot(roc2, col="red", add = TRUE )
plot(roc3, col="green", add = TRUE)
legend("bottomright", c("Logistics Regression", "Decision Tree", "Random Forest"), col = c("blue", "red", "green"), lty = 1)
```

